True versus apparent shapes of bow shocks

### 2018-02-27 papers/Papers1234/sec-conclusions.tex
Now we have two separate figures for the 000-400 fits

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/new-000-400-multi-fig}
  \caption[]{Example empirical determination of planitude and alatude
    for an observed bow shock.  Color scale and contours show an
    \textit{HST} H\(\alpha\) image (ACS F658N filter,
    \citealp{Bally:2006a}) of M42~000-400. Three different bows have
    been traced by hand on the image (red and white filled symbols):
    (\textit{a})~inner edge, (\textit{b})~ridge of maximum emission,
    and (\textit{c})~outer edge.  For each panel, the dark-colored
    circle shows the initial fit to the full set of points (white and
    red), using the algorithm described in
    Appendix~\ref{app:rcurv-empirical}.  The center of curvature and
    derived axis are shown by a small filled circle and dashed line in
    the same color. Lighter colored circles show three subsequent
    iterations where the fit is restricted to points within
    \(\pm \Delta\theta = \ang{75}\) of the axis.  The subset of points used in
    the final iteration is marked in red.  The perpendicular radii for
    the final iteration are shown by dotted lines. In panels
    \textit{b} and \textit{c} the iterations converge immediately, but
    in panel \textit{a} the iterations stably oscillate between two
    slightly different solutions. }
  \label{fig:000-400-fit}
\end{figure*}

\begin{figure}
  \includegraphics[width=\linewidth]{figs/000-400-planitude-alatude}
  \caption[]{Location in the projected planitude--alatude plane of the
    converged circle fits to the M42~000-400 bow.  For each solution,
    the two values of the alatude \(\Lambda'\), corresponding to
    \(R_{90}^+\) and \(R_{90}^-\), are joined by a vertical
    line. Large symbols show the results from the fits shown in
    Figure~\ref{fig:000-400-fit}, while small symbols show results for
    fits using \(\Delta\theta = \ang{60}\) instead of \ang{75}.}
  \label{fig:000-400-planitude-alatude}
\end{figure}

\section{Example application to observations}
\label{sec:obs}

As an example of measuring the projected planitude and alatude of a
real bow shock, in Figure~\ref{fig:000-400-fit} we present an analysis
of the H\(\alpha\) emission arc associated with the proplyd M42~000-400 in
the west of the Orion Nebula \citep{Bally:2000a},\footnote{%
  The same object is listed as 4596-400 in some catalogs, such as
  \citet{Ricci:2008a}.  } %
which was used as an archetype of the bow shape in
Figure~\ref{fig:bow-terminology}.  To give an idea of the systematic
uncertainties and sensitivity to subjective choices, three different
tracings of the bow shape are considered: the peak of the emission arc
(``ridge''), and its inner and outer edges
(Fig.~\ref{fig:000-400-fit}\textit{a}--\textit{c}).  In all three
cases, we placed the points that define the bow by eye, using
SAOImage~DS9 in a similar fashion to in Figure~\ref{fig:meyer-trace},
and guided by the image contours.\footnote{%
  In the case of the ``ridge'' method at least, it is possible to
  automate this step, which we will discuss in detail in a following
  paper. } %
The principal hindrance to an accurate tracing of the bow shape in
this object is the strong and variable nebular background emission,
which particularly affects the far wing on the right hand side of the
image, where a bright background filament is superimposed on the bow.
